https://cran.r-project.org/web/packages/huxtable/vignettes/huxtable.html


Introduction to Huxtable
David Hugh-Jones
2020-01-07
Introduction
About this document
Huxtable
Installation
Getting started
Changing the look and feel
Huxtable properties
Tidyverse syntax
Getting properties
Editing content
Changing and adding content
Editing content the base R way
Editing content the dplyr way
More formatting
Number format
Automatic formatting
Escaping HTML or LaTeX
Width and cell wrapping
Adding row and column names
Merging cells
Quick themes
Selecting rows, columns and cells
Row and column functions
Conditional formatting
Creating a regression table
Output to different formats
Automatic pretty-printing of data frames
Using huxtables in knitr and rmarkdown
Quick output commands
End matter
h	 	 	 	 	 
 	 	 	 
 	u	 	 	 	 
 	 	x	t	 
 	a	 	b	 
 	 	 	l	 	e
Introduction
About this document
This is the introductory vignette for the R package ‘huxtable’, version 4.7.1. A current version is available on the web in HTML or PDF format.

Huxtable
Huxtable is a package for creating text tables. It is powerful, but easy to use. Huxtable’s features include:

Export to LaTeX, HTML, Microsoft Word, Microsoft Excel, Microsoft Powerpoint, RTF and Markdown
Easy integration with knitr and rmarkdown documents
Formatted on-screen display
Multirow and multicolumn cells
Fine-grained control over cell background, spacing, alignment, size and borders
Control over text font, style, size, colour, alignment, number format and rotation
Table manipulation using standard R subsetting, or dplyr functions like filter and select
Easy conditional formatting based on table contents
Quick table themes
Automatic creation of regression output tables with the huxreg function
We will cover all of these features below.

Installation
If you haven’t already installed huxtable, you can do so from the R command line:
```{r}


install.packages('huxtable')
```
Getting started
A huxtable is an R object representing a table of text. You already know that R can represent a table of data in a data frame. For example, if mydata is a data frame, then mydata[1, 2] represents the the data in row 1, column 2, and mydata$start_time is all the data in the start_time column.

A huxtable is just a data frame with some extra properties. So, if myhux is a huxtable, then myhux[1, 2] represents the data in row 1 column 2, as before. But this cell will also have some other properties - for example, the font size of the text, or the colour of the cell border.

To create a huxtable, use the function huxtable, or hux for short. This works very much like data.frame:
```{r}


library(huxtable)
ht <- hux(
        Employee     = c('John Smith', 'Jane Doe', 'David Hugh-Jones'), 
        Salary       = c(50000L, 50000L, 40000L),
        add_colnames = TRUE
      )
```
You can convert a data frame to a huxtable with as_hux.

data(mtcars)
car_ht <- as_hux(mtcars)
If you look at a huxtable in R, it will print out a simple representation of the data. Notice that we’ve added the column names to the data frame itself, using the add_colnames argument to hux. We’re going to print them out, so they need to be part of the actual table. NB: This means that the data will start on row 2 of the huxtable, and the column names will be row 1.

print_screen(ht)     # on the R command line, you can just type "ht"
##   Employee            Salary  
##   John Smith           50000  
##   Jane Doe             50000  
##   David Hugh-Jones     40000  
## 
## Column names: Employee, Salary
To print a huxtable as LaTeX or HTML, just call print_latex or print_html. In knitr documents, like this one, you can simply evaluate the huxtable:

ht
Employee	Salary
John Smith	50000
Jane Doe	50000
David Hugh-Jones	40000
Changing the look and feel
Huxtable properties
The default output is a plain table. Let’s make it smarter. We’ll make the table headings bold, draw a line under the header row, add some horizontal space to the cells, and change the number formatting.

To do this, we will set some properties on the table cells. You set properties by assigning to the property name, just as you assign names(x) <- new_names in base R. The following commands assign the value 10 to the right_padding and left_padding properties, for all cells in ht:

right_padding(ht) <- 10
left_padding(ht)  <- 10
We can set the number_format property to change how numbers are displayed:

number_format(ht) <- 2    # 2 decimal places
To assign properties to just some cells, you use subsetting, as in base R. So, to make the first row of the table bold and give it a bottom border, we do:

bold(ht)[1, ]          <- TRUE
bottom_border(ht)[1, ] <- 1
After these changes, our table looks smarter:

ht
Employee	Salary
John Smith	50000.00
Jane Doe	50000.00
David Hugh-Jones	40000.00
So far, all these properties have been set at cell level. Different cells can have different alignment, text formatting and so on. By contrast, caption is a table-level property. It only takes one value, which sets a table caption.

caption(ht) <- 'Employee table'
ht
Employee table
Employee	Salary
John Smith	50000.00
Jane Doe	50000.00
David Hugh-Jones	40000.00
As well as cell properties and table properties, there is also one row property, row_height, and one column property, col_width.

The table below shows a complete list of properties.

Huxtable properties
Cell Text	Cell	Row	Column	Table
bold	align	row_height	col_width	caption
escape_contents	background_color			caption_pos
font	bottom_border			height
font	bottom_border_color			label
font_size	bottom_border_style			latex_float
italic	bottom_padding			position
na_string	colspan			tabular_environment
number_format	left_border			width
rotation	left_border_color			
text_color	left_border_style			
wrap	left_padding			
right_border			
right_border_color			
right_border_style			
right_padding			
rowspan			
top_border			
top_border_color			
top_border_style			
top_padding			
valign			
Tidyverse syntax
If you prefer a tidyverse style of code, using the pipe operator %>%, then you can use set_* functions to set properties. These are named like set_xxx where xxx is the property name, for example set_bold for the bold property.

set_* functions return the modified huxtable, so you can chain them together like this:
```{r}


library(dplyr)
hux(
        Employee     = c('John Smith', 'Jane Doe', 'David Hugh-Jones'), 
        Salary       = c(50000, 50000, 40000),
        add_colnames = TRUE
      )                               %>%
      set_right_padding(10)           %>%
      set_left_padding(10)            %>% 
      set_bold(1, 1:2, TRUE)          %>% 
      set_bottom_border(1, 1:2, 1)    %>%
      set_align(1:4, 2, 'right')      %>%
      set_number_format(2)            %>% 
      set_caption('Employee table')
```
Employee table
Employee	Salary
John Smith	50000.00
Jane Doe	50000.00
David Hugh-Jones	40000.00
set_* functions for cell properties are called like this: set_xxx(ht, row, col, value) or like this: set_xxx(ht, value). If you use the second form, then the value is set for all cells. set_* functions for table properties are always called like set_xxx(ht, value).

There are also some useful convenience functions:

set_all_borders sets left, right, top and bottom borders for selected cells;
set_all_border_colors sets left, right, top and bottom border colors;
set_all_border_styles sets left, right, top and bottom border styles;
set_all_padding sets left, right, top and bottom padding (the amount of space between the content and the border);
set_outer_borders, set_outer_border_colors and set_outer_border_styles set an outer border around a rectangle of cells.
Getting properties
To get the current properties of a huxtable, just use the properties function without the left arrow:

```{r}
italic(ht)

```
##   Employee Salary
## 1    FALSE  FALSE
## 2    FALSE  FALSE
## 3    FALSE  FALSE
## 4    FALSE  FALSE
position(ht)
## [1] "center"
Editing content
Changing and adding content
You can treat a huxtable just like a data frame. If you want to change data in a cell, assign to that cell:

ht[3, 1] <- 'Jane Jones'
ht
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
To add a column, do, e.g.:

ht_with_roles <- ht
ht_with_roles$Role <- c("Role", "Admin", "CEO", "Dogsbody")
ht_with_roles
Employee table
Employee	Salary	Role
John Smith	50000.00	Admin
Jane Jones	50000.00	CEO
David Hugh-Jones	40000.00	Dogsbody
Notice that the third column doesn’t have the properties we set on the first two columns, like the bold first row and the underlining.

If we want new columns to copy properties from their neighbours, we can use cbind, a base R function that binds columns together. When you cbind huxtable objects, by default, cell properties are copied over from their neighbours:

ht_with_roles <- cbind(ht, c("Role", "Admin", "CEO", "Dogsbody"))
ht_with_roles
Employee table
Employee	Salary	Role
John Smith	50000.00	Admin
Jane Jones	50000.00	CEO
David Hugh-Jones	40000.00	Dogsbody
rbind works the same way:

rbind(ht, c("Yihui Xie", 100000))
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
Yihui Xie	100000.00
Notice how Yihui’s salary has got the same number formatting as the other employees. That’s because cell properties for the new row were copied from the row above.

Sometimes, you would like to insert rows or columns in the middle of a table. You can do this with rbind, but it is not very convenient:

to_insert <- hux(
        Role  = c("Admin", "CEO", "Dogsbody"),
        Hired = as.Date(c("2015-01-01", "2008-06-05", "2012-07-31")),
        add_colnames = TRUE
      ) %>% 
      set_bold(1, 1:2, TRUE) %>% 
      set_bottom_border(1, 1:2, TRUE)

cbind(ht[, 1], to_insert, ht[, 2:ncol(ht)])
Employee table
Employee	Role	Hired	Salary
John Smith	Admin	2015-01-01	50000.00
Jane Jones	CEO	2008-06-05	50000.00
David Hugh-Jones	Dogsbody	2012-07-31	40000.00
It’s more elegant to use huxtable’s add_columns function:

add_columns(ht, to_insert, after = 1)
Employee table
Employee	Role	Hired	Salary
John Smith	Admin	2015-01-01	50000.00
Jane Jones	CEO	2008-06-05	50000.00
David Hugh-Jones	Dogsbody	2012-07-31	40000.00
The after argument says where the second object should be inserted. after can also be a column name:

add_columns(ht, to_insert, after = "Employee")
Employee table
Employee	Role	Hired	Salary
John Smith	Admin	2015-01-01	50000.00
Jane Jones	CEO	2008-06-05	50000.00
David Hugh-Jones	Dogsbody	2012-07-31	40000.00
The function add_rows works in the same way.

Editing content the base R way
You can subset, sort and data-wrangle a huxtable just like a normal data frame. Cell and table properties will be carried over into subsets.

car_ht <- as_hux(mtcars)                
car_ht <- huxtable::add_rownames(car_ht, "Car")
# Select columns by name:
car_ht <- car_ht[, c("Car", "mpg", "cyl", "am")] 

# Order by number of cylinders:
car_ht <- car_ht[order(car_ht$cyl), ]

car_ht <- huxtable::add_colnames(car_ht)

# Pretty output, see below: 
theme_plain(car_ht[1:5,])
Car	mpg	cyl	am
Datsun 710	22.8	4	1
Merc 240D	24.4	4	0
Merc 230	22.8	4	0
Fiat 128	32.4	4	1
Editing content the dplyr way
You can also use dplyr functions to edit a huxtable:

car_ht <- as_hux(mtcars)
car_ht <- huxtable::add_rownames(car_ht, colname = "Car")

car_ht <- car_ht                                          %>%
      slice(1:10)                                         %>% 
      select(Car, mpg, cyl, hp)                           %>% 
      arrange(hp)                                         %>% 
      filter(cyl > 4)                                     %>% 
      rename(MPG = mpg, Cylinders = cyl, Horsepower = hp) %>% 
      mutate(kml = MPG/2.82)                              %>% 
      huxtable::add_colnames()                            

theme_plain(car_ht)
Car	MPG	Cylinders	Horsepower	kml
Valiant	18.1	6	105	6.42
Mazda RX4	21  	6	110	7.45
Mazda RX4 Wag	21  	6	110	7.45
Hornet 4 Drive	21.4	6	110	7.59
Merc 280	19.2	6	123	6.81
Hornet Sportabout	18.7	8	175	6.63
Duster 360	14.3	8	245	5.07
In general it is a good idea to prepare your data first, before styling it. For example, it was easier to sort the cars_mpg data by cylinder, before adding a row of column names.

More formatting
Number format
You can change how huxtable formats numbers using number_format. Set number_format to a number of decimal places. This affects any numbers found within the cell text.

htn <- hux(c(
        "Some numbers...", 
        11.003, 
        300, 
        12.02, 
        "12.1 **", 
        "mean 11.7 (se 2.3)"
      )) 

number_format(htn) <- 3
theme_plain(htn)
Some numbers...
11.003
300.000
12.020
12.100 **
mean 11.700 (se 2.300)
To align columns by decimal places, just set the align property to ".":

align(htn)[2:6, ] <- "." # not the first row

theme_plain(htn)
Some numbers...
11.003   
300.000   
12.020   
12.100 **
mean 11.700 (se 2.300)  
There is currently no true way to align cells by the decimal point in HTML, and only limited possibilities in TeX, so this works by right-padding cells with spaces. The output may look better if you use a fixed width font.

Automatic formatting
By default, when you create a huxtable using huxtable or as_huxtable, the package will guess defaults for number formatting and alignment, based on the type of data in your columns. Numeric data will be right-aligned or aligned on the decimal point; character data will be left aligned; and the package will try to set sensible defaults for number formatting. If you want to, you can turn this off with autoformat = FALSE:

my_data <- data.frame(
        Employee    = c("John Smith", "Jane Doe", "David Hugh-Jones"), 
        Salary      = c(50000L, 50000L, 40000L),
        Performance = c(8.9, 9.2, 7.8)  
      )

as_hux(my_data, add_colnames = TRUE) # with automatic formatting
Employee	Salary	Performance
John Smith	50000	8.9
Jane Doe	50000	9.2
David Hugh-Jones	40000	7.8
as_hux(my_data, add_colnames = TRUE, autoformat = FALSE) # no automatic formatting
Employee	Salary	Performance
John Smith	5e+04	8.9
Jane Doe	5e+04	9.2
David Hugh-Jones	4e+04	7.8
Escaping HTML or LaTeX
By default, HTML or LaTeX code will be escaped:

code_ht <- if (is_latex) hux(c("Some maths", "$a^b$")) else 
      hux(c("Copyright symbol", "&copy;"))

theme_plain(code_ht)
Copyright symbol
&copy;
To avoid this, set the escape_contents property to FALSE.

escape_contents(code_ht)[2, 1] <- FALSE

theme_plain(code_ht)
Copyright symbol
©
Width and cell wrapping
You can set table widths using the width property, and column widths using the col_width property. If you use numbers for these, they will be interpreted as proportions of the table width (or for width, a proportion of the width of the surrounding text). If you use character vectors, they must be valid CSS or LaTeX widths. The only unit both systems have in common is pt for points.

width(ht) <- 0.4
col_width(ht) <- c(.7, .3)
ht
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
It is best to set table width explicitly, then set column widths as proportions.

By default, if a cell contains long contents, it will be stretched. Use the wrap property to allow cell contents to wrap over multiple lines:

ht_wrapped <- ht
ht_wrapped[5, 1] <- "David Arthur Shrimpton Hugh-Jones"
wrap(ht_wrapped) <- TRUE
ht_wrapped
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
David Arthur Shrimpton Hugh-Jones	
Adding row and column names
Just like data frames, huxtables can have row and column names. Often, we want to add these to the final table. You can do this using either the add_colnames/add_rownames arguments to as_huxtable, or the add_colnames()/add_rownames() functions.

as_hux(mtcars[1:4, 1:4])                           %>% 
      huxtable::add_rownames(colname = "Car name") %>% 
      huxtable::add_colnames()
Car name	mpg	cyl	disp	hp
Mazda RX4	21  	6	160	110
Mazda RX4 Wag	21  	6	160	110
Datsun 710	22.8	4	108	93
Hornet 4 Drive	21.4	6	258	110
Merging cells
Sometimes you want a single cell to spread over more than one row or column: for example, if you want a heading that covers several different rows.

You can do this by calling merge_cells(ht, rows, cols). rows and cols should be a contiguous sequence of numbers. The rectangle of cells ht[rows, cols] will be merged.

When cells in a rectangle are merged, all cells apart from the top left one are hidden, along with any properties they have. So if you want to set cell properties, you have to target the top left cell.

Here, we’ll add some row and column headings to the mtcars dataset:

car_ht <- as_hux(mtcars)
car_ht <- huxtable::add_rownames(car_ht, colname = "Car")
car_ht <- car_ht %>% arrange(cyl) %>% select(1:4)
car_ht <- huxtable::add_colnames(car_ht)

car_ht <- cbind(cylinders = car_ht$cyl, car_ht)
car_ht$cylinders[1]   <- ""
car_ht$cylinders[2]   <- "Four cylinders"
car_ht$cylinders[13]  <- "Six cylinders"
car_ht$cylinders[20]  <- "Eight cylinders"

car_ht <- car_ht %>%  
  merge_cells(2:12, 1) %>% 
  merge_cells(13:19, 1) %>% 
  merge_cells(20:33, 1)


car_ht <- rbind(c("List of cars", "", "", "", ""), car_ht)
car_ht <- merge_cells(car_ht, 1, 1:5)
align(car_ht)[1, 1] <- "center"

car_ht <- theme_plain(car_ht)
right_border(car_ht)[1, 1] <- 0.4
bottom_border(car_ht)[21, 1] <- 0.4
car_ht
List of cars
Car	mpg	cyl	disp
Four cylinders	Datsun 710	22.8	4	108  
Merc 240D	24.4	4	147  
Merc 230	22.8	4	141  
Fiat 128	32.4	4	78.7
Honda Civic	30.4	4	75.7
Toyota Corolla	33.9	4	71.1
Toyota Corona	21.5	4	120  
Fiat X1-9	27.3	4	79  
Porsche 914-2	26  	4	120  
Lotus Europa	30.4	4	95.1
Volvo 142E	21.4	4	121  
Six cylinders	Mazda RX4	21  	6	160  
Mazda RX4 Wag	21  	6	160  
Hornet 4 Drive	21.4	6	258  
Valiant	18.1	6	225  
Merc 280	19.2	6	168  
Merc 280C	17.8	6	168  
Ferrari Dino	19.7	6	145  
Eight cylinders	Hornet Sportabout	18.7	8	360  
Duster 360	14.3	8	360  
Merc 450SE	16.4	8	276  
Merc 450SL	17.3	8	276  
Merc 450SLC	15.2	8	276  
Cadillac Fleetwood	10.4	8	472  
Lincoln Continental	10.4	8	460  
Chrysler Imperial	14.7	8	440  
Dodge Challenger	15.5	8	318  
AMC Javelin	15.2	8	304  
Camaro Z28	13.3	8	350  
Pontiac Firebird	19.2	8	400  
Ford Pantera L	15.8	8	351  
Maserati Bora	15  	8	301  
Quick themes
Huxtable comes with some predefined themes for formatting. You’ve already seen theme_plain. Other options include theme_basic and (for fun) theme_mondrian:

theme_mondrian(ht)
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
The “themes” vignette shows all the available themes.

Selecting rows, columns and cells
Row and column functions
If you use the set_* style functions, huxtable has some convenience functions for selecting rows and columns. To select all rows, or all columns, use everywhere in the row or column specification. To select the last n rows or columns, use final(n).

You can also use dplyr functions like starts_with(), contains(), and matches() to specify columns by column name. For a full list of these functions, see ?select_helpers.

ht %>% set_background_color(everywhere, starts_with("S"), "orange")
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
Lastly, remember that you can set a property for every cell by omitting the row and col arguments, like this: set_background_color(ht, "orange").

Conditional formatting
When you want to apply different formatting to different cells, you can use the map_xxx functions.

For example, we could create a striped table like this:

ht %>% map_background_color(by_rows("grey90", "grey95"))
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
Or, we could apply a text color to our cars based on their ecological performance:

car_ht %>% map_text_color(everywhere, 3, 
        by_ranges(c(15, 25), c("red", "darkgreen", "green"))
      )
List of cars
Car	mpg	cyl	disp
Four cylinders	Datsun 710	22.8	4	108  
Merc 240D	24.4	4	147  
Merc 230	22.8	4	141  
Fiat 128	32.4	4	78.7
Honda Civic	30.4	4	75.7
Toyota Corolla	33.9	4	71.1
Toyota Corona	21.5	4	120  
Fiat X1-9	27.3	4	79  
Porsche 914-2	26  	4	120  
Lotus Europa	30.4	4	95.1
Volvo 142E	21.4	4	121  
Six cylinders	Mazda RX4	21  	6	160  
Mazda RX4 Wag	21  	6	160  
Hornet 4 Drive	21.4	6	258  
Valiant	18.1	6	225  
Merc 280	19.2	6	168  
Merc 280C	17.8	6	168  
Ferrari Dino	19.7	6	145  
Eight cylinders	Hornet Sportabout	18.7	8	360  
Duster 360	14.3	8	360  
Merc 450SE	16.4	8	276  
Merc 450SL	17.3	8	276  
Merc 450SLC	15.2	8	276  
Cadillac Fleetwood	10.4	8	472  
Lincoln Continental	10.4	8	460  
Chrysler Imperial	14.7	8	440  
Dodge Challenger	15.5	8	318  
AMC Javelin	15.2	8	304  
Camaro Z28	13.3	8	350  
Pontiac Firebird	19.2	8	400  
Ford Pantera L	15.8	8	351  
Maserati Bora	15  	8	301  
by_rows and by_ranges are mapping functions.

by_rows applies different properties to different rows in sequence.

by_ranges divides its input into ranges, and outputs colours based on that, like the base R function cut.

Above, we mapped all numbers below 15 to "red", numbers between 15 and 25 to "darkgreen" and numbers above 25 to "green".

The syntax of all map_xxx functions is map_xxx(ht, row, col, fn). ht is the huxtable, and fn is the mapping function starting with by. row and col are optional row and column specifiers, just the same as for set_xxx.

You can also apply properties for cells that match a string, using the by_regex mapping function:

ht %>% map_bold(by_regex('Jones' = TRUE))
Employee table
Employee	Salary
John Smith	50000.00
Jane Jones	50000.00
David Hugh-Jones	40000.00
There is a map_xxx function for each property xxx. See the help pages for other mapping functions.

Creating a regression table
To create a table of regressions, use huxreg:

lm1 <- lm(mpg ~ cyl, mtcars)
lm2 <- lm(mpg ~ hp, mtcars)
lm3 <- lm(mpg ~ cyl + hp, mtcars)

huxreg(lm1, lm2, lm3)
(1)	(2)	(3)
(Intercept)	37.885 ***	30.099 ***	36.908 ***
(2.074)   	(1.634)   	(2.191)   
cyl	-2.876 ***	        	-2.265 ***
(0.322)   	        	(0.576)   
hp	        	-0.068 ***	-0.019    
        	(0.010)   	(0.015)   
N	32        	32        	32        
R2	0.726    	0.602    	0.741    
logLik	-81.653    	-87.619    	-80.781    
AIC	169.306    	181.239    	169.562    
*** p < 0.001; ** p < 0.01; * p < 0.05.
For more information see the “huxreg” vignette.

Output to different formats
Automatic pretty-printing of data frames
If you load huxtable within a knitr document, it will automatically format data frames for you:

head(mtcars)
mpg	cyl	disp	hp	drat	wt	qsec	vs	am	gear	carb
21  	6	160	110	3.9 	2.62	16.5	0	1	4	4
21  	6	160	110	3.9 	2.88	17  	0	1	4	4
22.8	4	108	93	3.85	2.32	18.6	1	1	4	1
21.4	6	258	110	3.08	3.21	19.4	1	0	3	1
18.7	8	360	175	3.15	3.44	17  	0	0	3	2
18.1	6	225	105	2.76	3.46	20.2	1	0	3	1
If you don’t want this, you can turn it off by setting the huxtable.knit_print_df option:

options(huxtable.knit_print_df = FALSE)

head(mtcars) # back to normal
##                    mpg cyl disp  hp drat    wt  qsec vs am gear carb
## Mazda RX4         21.0   6  160 110 3.90 2.620 16.46  0  1    4    4
## Mazda RX4 Wag     21.0   6  160 110 3.90 2.875 17.02  0  1    4    4
## Datsun 710        22.8   4  108  93 3.85 2.320 18.61  1  1    4    1
## Hornet 4 Drive    21.4   6  258 110 3.08 3.215 19.44  1  0    3    1
## Hornet Sportabout 18.7   8  360 175 3.15 3.440 17.02  0  0    3    2
## Valiant           18.1   6  225 105 2.76 3.460 20.22  1  0    3    1
Using huxtables in knitr and rmarkdown
If you use knitr and rmarkdown in RStudio, huxtable objects should automatically display in the appropriate format (HTML, LaTeX, or RTF).

Huxtable needs some LaTeX packages for LaTeX output. The function report_latex_dependencies() will print out a set of usepackage{...} statements. If you use Sweave or knitr without rmarkdown, you can use this function in your LaTeX preamble, to load the packages you need.

If you want to create Word or Powerpoint documents, install the flextable package from CRAN. Huxtables can then be automatically printed in Word documents. Or you can convert them to flextable objects and include them in Word or Powerpoint documents. Similarly, to print tables in an Excel spreadsheet, install the openxlsx package See ?as_flextable and ?as_Workbook for more details.

You can print a huxtable on screen by typing its name at the command line. Borders, column and row spans and cell alignment are shown. If the crayon package is installed, and your terminal or R IDE supports it, border, text and background colours are also displayed.

print_screen(ht)
##         Employee table         
##   Employee             Salary  
## ───────────────────────────────
##   John Smith         50000.00  
##   Jane Jones         50000.00  
##   David Hugh-Jones   40000.00  
## 
## Column names: Employee, Salary
If you need to output to another format, file an issue request on Github.

Quick output commands
Sometimes you quickly want to get your data into a document. To do this you can use huxtable functions starting with quick_:

Command	Output
quick_pdf	PDF document
quick_docx	Word document
quick_html	HTML web page
quick_xlsx	Excel spreadsheet
quick_pptx	Powerpoint presentation
quick_rtf	RTF document
quick_latex	LaTeX document
These are called with one or more huxtable objects (or objects which can be turned into a huxtable, such as data frames). A new document of the appropriate type will be created and opened. By default the file will be in the current directory, under a name like e.g. huxtable-output.pdf. If the file already exists, you’ll be asked to confirm the overwrite.

quick_pdf(mtcars) 
quick_pdf(mtcars, file = 'motorcars data.pdf')
End matter
For more information, see the website or github.