
Comparison of two distribtions

the k-s test returns a D statistic and a p-value corresponding to the D statistic. 
The D statistic is the absolute max distance (supremum) between the CDFs of the two samples. 
The closer this number is to 0 the more likely it is that the two samples were drawn from the same distribution.


Feed vs Feed
```{r}
RawPSD1 <- read_csv(here("03_code/01_code-output","RawPSD.csv"))
```


```{r}
ks.test(cumsum(RawPSD1$Feed13MeanPct), cumsum(RawPSD1$Feed14MeanPct))

```

OS vs OS
```{r}
ks.test(cumsum(RawPSD1$OS13MeanPct), cumsum(RawPSD1$OS14MeanPct))
```

US vs US
```{r}
ks.test(cumsum(RawPSD1$US13MeanPct), cumsum(RawPSD1$US14MeanPct))
```
SC13
Feed Vs OS
```{r}
ks.test(cumsum(RawPSD1$Feed13MeanPct), cumsum(RawPSD1$OS13MeanPct))
```

SC14
Feed Vs OS
```{r}
ks.test(cumsum(RawPSD1$Feed14MeanPct), cumsum(RawPSD1$OS14MeanPct))
```
comparison between feed vs OS for that of sc13 vs sc14 looks wrong..they are exactly the same... when compared to the OS vs US results



SC13
OS Vs US
```{r}
ks.test(cumsum(RawPSD1$OS13MeanPct), cumsum(RawPSD1$US13MeanPct))
```

SC14
OS Vs US
```{r}
ks.test(cumsum(RawPSD1$OS14MeanPct), cumsum(RawPSD1$US14MeanPct))
```
