---
output:
  pdf_document: default
  html_document: default
---
# side by side plots

Aim is not to reprint plot's axes for each plotted side-by-side plot as they are the same..can be a common axis/axes.


https://stackoverflow.com/questions/13649473/add-a-common-legend-for-combined-ggplots
## method 1


```{r, include = FALSE}
#Function here::here to help with file paths relative to the project folder:
library("here")
```


```{r,include = FALSE }
#attache rpackages from central location:
source(here::here("02_rpackages",'projectpackages.R'))

```


```{r include = FALSE}

options(qwraps2_markup = 'markdown')

knitr.table.format = "latex" #global option for tables. can still set any in each kable function.

```
<br><br><br><br>

Each test's feed stream PSD results were first compared to confirm that their distributions were simmilar to allow for comparitive statictics.  


```{r global_options, R.options=knitr::opts_chunk$set(warning=FALSE, message=FALSE)}
```
```{r unmodeled_PSDdata_in, echo=FALSE}
#results generated in screentest-19oct2014.R
feedraw_psd <- read.csv(file = here::here("03_code/01_code-output","feedraw_psd.txt"))
OSraw_psd <- read.csv(file = here::here("03_code/01_code-output","OSraw_psd.txt"))
USraw_psd <- read.csv(file = here::here("03_code/01_code-output","USraw_psd.txt"))

#this code is duplicated (convert to long data and plots) in "screentest-19oct2014.Rmd". here for report inclusion, there for prior checking.

long_feedraw_psd <- feedraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")
long_OSraw_psd <- OSraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")  
long_USraw_psd <- USraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")


plot.Feedraw_psd <- ggplot(long_feedraw_psd, aes(sieve, probability, colour = stream)) +
  geom_line()+
  ggtitle("Feed streams unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9))
  #annotate(extra text any location on plot) geom = "text", x = 1.00, y = 1.00,

plot.OSraw_psd <- ggplot(long_OSraw_psd, aes(sieve, probability, colour = stream)) +
  geom_line()+
  ggtitle("OverSize streams unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9))

plot.USraw_psd <- ggplot(long_USraw_psd, aes(sieve, probability, colour = stream)) +
  geom_line()+
  ggtitle("Undersize stream unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9))


ggsave(file=here("05_fig_output","feedraw_psd.pdf"), plot.Feedraw_psd, width=10, height=8)
ggsave(file=here("05_fig_output","OSraw_psd.pdf"), plot.OSraw_psd, width=10, height=8) 
ggsave(file=here("05_fig_output","USraw_psd.pdf"), plot.USraw_psd, width=10, height=8)

```

```{r}
# package name: patchwork (side by side plots)
combined.plot_raw_psd <- plot.Feedraw_psd + plot.OSraw_psd + plot.USraw_psd & theme(legend.position = "bottom")
combined.plot_raw_psd + plot_layout(guides = "collect")

```

***

# Method 2

Each test's feed stream PSD results were first compared to confirm that their distributions were simmilar to allow for comparitive statictics.  



```{r , echo=FALSE}
#results generated in screentest-19oct2014.R
feedraw_psd <- read.csv(file = here::here("03_code/01_code-output","feedraw_psd.txt"))
OSraw_psd <- read.csv(file = here::here("03_code/01_code-output","OSraw_psd.txt"))
USraw_psd <- read.csv(file = here::here("03_code/01_code-output","USraw_psd.txt"))

#this code is duplicated (convert to long data and plots) in "screentest-19oct2014.Rmd". here for report inclusion, there for prior checking.

long_feedraw_psd <- feedraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")
long_OSraw_psd <- OSraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")  
long_USraw_psd <- USraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")

```





difference in code starts here:

```{r}
#combine the datasets:
PSD_raw_psd_allStreams <- rbind(long_feedraw_psd,long_OSraw_psd,long_USraw_psd)

PSD_raw_psd_allStreams <- data.frame(PSD_raw_psd_allStreams,
                             Df = rep(c("Feed (unmodeled)","OS (unmod.)","US (unmod.)" ),
                                                      times=c(nrow(long_feedraw_psd),nrow(long_OSraw_psd),nrow(long_USraw_psd))))

outplot_all_unmoddled <- ggplot(PSD_raw_psd_allStreams, aes(sieve, probability, colour = stream)) +
  geom_line() +
  geom_point() +
  ggtitle("Feed streams unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df)


ggsave(here("05_fig_output","all_streams_preModelling.pdf"), outplot_all_unmoddled, width=10, height=8)
```
method 2 is perfect for this application:

+ x and y same for all plots
+ can combine with row bing...in this case no problem..with cbind will be a proble where different models(RR and GGS) have diffrenrows due to logs.



# Method 3
try to combine 3 PSD with 3 cummulative PSDs

```{r}

#combine the datasets for plotting side-by-side:

PSD_raw_psd_allStreams <- rbind(long_feedraw_psd,long_OSraw_psd,long_USraw_psd)

#PSD_cum_raw_psd_allStreams <- cumsum(PSD_raw_psd_allStreams)

PSD_raw_psd_allStreams <- data.frame(PSD_raw_psd_allStreams,
                             Df = rep(c("Feed (unmodeled)","OS (unmod.)","US (unmod.)" ),
                                                      times=c(nrow(long_feedraw_psd),nrow(long_OSraw_psd),nrow(long_USraw_psd))))

(outplot_all_unmoddled <- ggplot(PSD_raw_psd_allStreams, aes(sieve, cumsum(probability), colour = stream)) +
  geom_line(size = 1) +
  geom_point() +
  ggtitle("Unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=10)) +
  facet_wrap(~Df))

```

```{r eval=TRUE, echo=FALSE, fig.align='center', fig.cap='...', include=TRUE, out.width='50%'}
knitr::include_graphics(here::here("05_fig_output",'allStreamsPreModelling.pdf'))
```


```{r, echo = FALSE, eval = TRUE, include = TRUE, out.width='50%', fig.align='center', fig.cap='...'}
knitr::include_graphics(here::here("05_fig_output",'allStreamsCummulativePreModelling.pdf'))
```








