---
output:
  pdf_document: default
  html_document: default
---
This file imports the means of the streams from the 5 decks on the each of the two screens in the plant.
import from 01_ImportWrangle2Means19Oct2014.Rmd

```{r, include = FALSE}
library("here")
source(here::here("02_rpackages",'projectpackages.R'))

knitr::opts_chunk$set(echo = FALSE, warning=FALSE,message=FALSE)
knitr::opts_chunk$set(fig.align="center") #default align for figures
knitr.table.format = "latex" #global option for tables. can still set any in each kable function.
```


import wrangled means
```{r}
unmod2 <- read_csv(here("03_code/01_code-output","RawPSD.csv"))
```


```{r}
# change underpan from 0 to 1 micron to avoid log0 
#im sure this step can be removed as this line will be remove for the moddeling anyway...
  tmp <- rev(unmod2$sieve)
 if(tmp[1]  < 1) {
    tmp[1] <- 1
    unmod2$sieve <- rev(tmp)
  }

```




```{r}
unmodlong2 <- unmod2 %>% 
  pivot_longer(-sieve, names_to= "stream" , values_to = "probability")%>% 
 group_by(stream) %>% 
  mutate (cumret = cumsum(probability))

  tmp <- rev(unmodlong2$cumret)
 if(tmp[1] - 1 < 1e-12) {
    tmp[1] <- 1
    unmodlong2$cumret <- rev(tmp)
  }

unmodlong2$cumpass <- (1-unmodlong2$cumret)  


# unmodungroup <- unmodlong2 %>% 
#   ungroup()

#   tmp <- rev(unmodungroup$cumret)
#   
# if(tmp[1] - 1 < 1e-12) {
#     tmp[1] <- 1
#     unmodungroup$cumret <- rev(tmp)
#   }




unmodlongDF <- data.frame(unmodlong2,
                             Df = rep(c("Feed (unmodeled)","OS (unmod.)","US (unmod.)" ),                                                                         times=c(2,2,2))) #the 222 :the df has 2 feeds 2 oversize 2 undersize factors that gets repeated.
```


```{r}
(plotUnmod <- ggplot(unmodlongDF, aes(sieve, probability, colour = stream)) +
  geom_line(size = 1) +
  geom_point() +
  ggtitle(" unmoddeled solids frequency distributions.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df))


(plotUnmodCum <- ggplot(unmodlongDF, aes(sieve, cumpass, colour = stream)) +
  geom_line(size = 1) +
  geom_point() +
  ggtitle(" unmoddeled solids frequency distributions.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df))

ggsave(here("05_fig_output","allStreamsPreModelling.pdf"), plotUnmod, width=10, height=8)

ggsave(here("05_fig_output","allStreamsCummulativePreModelling.pdf"), plotUnmodCum, width=10, height=8)
```


```{r}
#remove last row in wide tibble before converting to tidy datat with subsequint cummulative calc

cumsum<- unmod2 %>% 
  dplyr::select(-sieve) %>% 
  cumsum() %>% 
  dplyr::slice(1:11) 

sieveSliced<- unmod2 %>% 
  dplyr::select(sieve) %>% 
  dplyr::slice(1:11)

#join the x and y back into one tibble
SlicedCumsum <- cbind(sieveSliced ,cumsum)
```


```{r}
#Pivot longer then group_by stream and calculate the cumulative %retained "cumret".

longCumsum <- SlicedCumsum %>% 
  pivot_longer(-sieve, names_to= "stream" , values_to = "cumret")%>% 
 group_by(stream) %>% 
  mutate (cumpass = 1- cumret)

```


```{r}
#Rosin Rammler plot

longCumsumDF <- data.frame(
  longCumsum, Df = rep(c("Feed (modeled)","OS (mod.)","US (mod.)" ), 
                       times=c(2,2,2)))

(plotModRR <- ggplot(longCumsumDF, 
                        aes(log(sieve), log(-log(1-cumpass)), colour = stream)) +
  # geom_line(size = 1) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle(" Rosin Rammler Modelled distributions.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df))


```


```{r}
longCumsumDF <- data.frame(
  longCumsum, Df = rep(c("Feed (modeled)","OS (mod.)","US (mod.)" ), times=c(2,2,2)))

(plotModGGS <- ggplot(longCumsumDF, 
                        aes(log(sieve), log(cumpass), colour = stream)) +
  # geom_line(size = 1) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)+
  ggtitle(" Gates-Gaudin-Schumann Modelled distributions.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df))



ggsave(here("05_fig_output","RRModelled.pdf"), plotModRR, width=10, height=8)

ggsave(here("05_fig_output","GGSModelled.pdf"), plotModGGS, width=10, height=8)

```

still trying to the predictions
```{r}
c <- 1e-12


#functions
RosinRammler <- function(df) {
  lm(log(-log(1-cumpass + c)) ~ log(sieve),
    data = df
    )
}

GatesGaudinSchumann <- function(df) {
  lm(log(cumpass) ~ log(sieve), 
     data = df
    )
}
```
trying to replace the model function above ..the "df" part is confusing where does the data come from.
so now below i try hadleys way :P



```{r}
Reg <- longCumsumDF %>% 
  group_by(stream) %>% 
  nest() %>% 
 mutate(
   RRmodels = lapply(data, RosinRammler),# "RRmodels" column will be created in the mutate. RosinRammler defined function is applied to the data "data" within (pipe opperator)  "longCumSumDF" the data frame.
   tidied_RR = map (RRmodels, tidy),
   glanced_RR = map(RRmodels, glance),
   augmented_RR = map (RRmodels, augment),

  #GGS model
   GGS_models = lapply(data, GatesGaudinSchumann),# "GGS_models" column will be created in the mutate.
   tidied_GGS = map (GGS_models, tidy),
   glanced_GGS = map(GGS_models, glance))#,
   # augmented_GGS = map (GGS_models, augment)) %>% 
   #  mutate_if(is.numeric, list(~na_if(., abs(Inf))))




```

predicting the fraction of material that will pass a certain screen size:
```{r}
#https://stackoverflow.com/questions/52331501/using-predict-function-for-new-data-along-with-tidyverse

#Small constant to avoid log of zero
c <- 1e-12
# the screen size we want to predict at is 250 um
newdat <- data.frame(sieve = c(250))
library(tidyverse)
preds <- longCumsumDF %>%
  group_by(stream) %>%
  nest() %>%
 
  mutate(model1  = purrr::map(.x = data, .f = ~ lm(log(cumpass) ~ log(sieve), data = .))) %>%
  mutate(model2  = purrr::map(.x = data, .f = ~ lm(log(-log(1-cumpass+c)) ~ log(sieve), data = .))) %>%
 
  mutate(logPred = purrr::map(.x = model1, ~ predict(., newdat))) %>%
  mutate(loglogPred = purrr::map(.x = model2, ~ predict(., newdat))) %>%
 
  select(stream,loglogPred, logPred,) %>%
  unnest() %>%   #%>% cbind(newdat = newdat) 
  
  mutate(PredGGS = exp(logPred)) %>% 
  mutate(PredRR = 1-exp(-exp(loglogPred))) %>% 
  
  select(stream,PredRR, PredGGS, loglogPred, logPred, ) 

write.csv(preds,here::here("03_code/01_code-output","modelOutput.csv"),row.names = FALSE)


preds
#yay it works !!!
```

```{r echo = FALSE, results='asis'}


tblpred <- knitr::kable(preds,
                        "latex",caption = "Modelled cummulative passing 250um" ,
                        escape = F,booktabs = T, 
                        digits = c(0,2,2,2,2)) %>% 
  column_spec(1, width = "3cm") %>% 
  column_spec(2:5, width = "1.5cm") %>% 
  kable_styling(c("striped", "bordered")) %>% 
#saving immage
 as_image(width = 4)
  
   save_kable(here::here("03_code/01_code-output","tblpred"), 
                 file_format = "jpeg", keep_pdf = F)




save_kable(tblpred, here::here("03_code/01_code-output","tblpred"), bs_theme = "simplex", self_contained = TRUE,
  extra_dependencies = NULL,  latex_header_includes = NULL,
  keep_tex = FALSE)
```



```{r}
tidiedRR <- Reg %>% 
  unnest(tidied_RR) %>% 
  dplyr::select(stream,term, estimate)

tidiedGGS <- Reg %>% 
  unnest(tidied_GGS) %>% 
  dplyr::select(stream,term, estimate)

write.csv(tidiedRR, file = here("03_code/01_code-output","CoefRR.csv"), row.names = FALSE)
write.csv(tidiedGGS, file = here("03_code/01_code-output","CoefGGS.csv"), row.names = FALSE)



glancedRR <- Reg %>% 
  unnest(glanced_RR)

glancedGGS <- Reg %>% 
  unnest(glanced_GGS)
```



extra r^2 chart
```{r}
#https://drsimonj.svbtle.com/running-a-model-on-separate-groups

glancedRR %>% 
  ggplot(aes(x = factor(stream), y = r.squared)) +
    geom_bar(stat = "identity") +
    labs(x = "Stream", y = expression(R^{2}))


```
statistical measures of model fit.
CLeaning up the glanced data and only selecting the output required for presentation.
Coefficient of determination `R^2`.(i tried latex formatting for the R2 not yet successful)
```{r}
#coeficient of determinant
R2RR <- glancedRR %>% 
      dplyr::select(stream, R2 = r.squared, adj.R2 = adj.r.squared, p.value, AIC)#conduct select and rename in one step with dplyr::select()

R2GGS <- glancedGGS %>% 
      dplyr::select(stream, R2 = r.squared, adj.R2 = adj.r.squared, p.value, AIC)

write.csv(R2RR, here("03_code/01_code-output","R2RR.csv"),row.names = FALSE)
write.csv(R2GGS, here("03_code/01_code-output","R2GGS.csv"),row.names = FALSE)
#written csvs are draw in by ~03_code/tableR2.Rmd

```



```{r}

```






