# Model Section

Automating the selection of the best model for each stream
create a list of model outputs (adjR2) for every stream,
thus make a frame for every stream that contains a list of the model outputs, then rank or Order and select (slice) the best.

Preparing for model selection by stream:
it will be more efficient to list the model outputs within each stream.
followed  group and nest, then arrange so the best performining model is the first (on top). then slice the best for use in the efficiency determination part.




```{r}
#draw in data required for modelsection.
#data generated in precurser file: "Modeling
Screen13modelOutput <- read.csv(here::here("03_code/01_code-output","Screen13modelOutput.csv"))
Screen14modelOutput <- read.csv(here::here("03_code/01_code-output","Screen14modelOutput.csv"))

RegAll <- readRDS(here::here("03_code/01_code-output","Reg.Rdata"))



```

```{r}
#remove the log predictions

Screen13modelOutput <- Screen13modelOutput %>% 
  dplyr::select(stream,PredRR,PredGGS)

Screen14modelOutput <- Screen14modelOutput %>% 
  dplyr::select(stream,PredRR,PredGGS)
```



```{r}
glanced_Reg_allModels  <- RegAll %>% 
  dplyr::select (stream ,glanced_RR, glanced_GGS)
#joins model selection criteria and the predictions that will be used once the model is selected.


glancedReg13 <- RegAll %>% 
  dplyr::filter(stringr::str_detect(stream,'13')) %>% 
  dplyr::select (stream ,glanced_RR, glanced_GGS)

glancedReg14 <- RegAll %>% 
  dplyr::filter(stringr::str_detect(stream,'13')) %>% 
  dplyr::select (stream ,glanced_RR, glanced_GGS)

```

model1 <- RR
model2 <- GGS

```{r}
modellist <- c("RR","GGS") # vector of the models will improve automation (next time do this earlier on in the project)
```


There are three streams per screen stack, thus best model selection must occur 3 times.
Starting with SCreen13 Feed:


#########################################
# SCREEN 13
## FEED
##########################################
```{r}
F13Pred <- Screen13modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'Feed')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) #i just chose "Preds" as abr. for Predictions. My code Currently only works with 1 screen size in the model selection automation code im writing here. There aremany packegaes that came save time here..more to read and select and implement.

F13RRCoefD <- glancedReg13%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'Feed')) %>%  
    dplyr::select( glanced = glanced_RR)

 F13GGSCoefD <- glancedReg13%>% 
  ungroup() %>% 
   dplyr::slice(1) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
F13modelsArranged <-  rbind(F13RRCoefD,F13GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = F13Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestF13 <- F13modelsArranged %>% 
  dplyr::slice(1)

write.csv(BestF13,here::here("03_code/01_code-output", "BestF13.csv"))
```


# SCREEN 13
## OVERSIZE

```{r}
OS13Pred <- Screen13modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'OS')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) 

OS13RRCoefD <- glancedReg13%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'OS')) %>%  
    dplyr::select( glanced = glanced_RR)

 OS13GGSCoefD <- glancedReg13%>% 
  ungroup() %>% 
   dplyr::filter(stringr::str_detect(stream,'OS')) %>%
   # dplyr::slice(3) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
OS13modelsArranged <-  rbind(OS13RRCoefD,OS13GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = OS13Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestOS13 <- OS13modelsArranged %>% 
  dplyr::slice(1)

write.csv(BestOS13,here::here("03_code/01_code-output", "BestOS13.csv"))

```

# SCREEN 13
## UNDERSIZE

```{r}
US13Pred <- Screen13modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'US')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) 

US13RRCoefD <- glancedReg13%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'US')) %>%  
    dplyr::select( glanced = glanced_RR)

 US13GGSCoefD <- glancedReg13%>% 
  ungroup() %>% 
   dplyr::filter(stringr::str_detect(stream,'US')) %>%
   # dplyr::slice(5) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
US13modelsArranged <-  rbind(US13RRCoefD,US13GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = US13Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestUS13 <- US13modelsArranged %>% 
  dplyr::slice(1)

write.csv(BestUS13,here::here("03_code/01_code-output", "BestUS13.csv"))

```
#########################################
# SCREEN 14
## FEED
##########################################
```{r}
F14Pred <- Screen14modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'Feed')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) #i just chose "Preds" as abr. for Predictions. My code Currently only works with 1 screen size in the model selection automation code im writing here. There aremany packegaes that came save time here..more to read and select and implement.

F14RRCoefD <- glancedReg14%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'Feed')) %>%  
    dplyr::select( glanced = glanced_RR)

 F14GGSCoefD <- glancedReg14%>% 
  ungroup() %>% 
   dplyr::slice(1) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
F14modelsArranged <-  rbind(F14RRCoefD,F14GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = F14Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestF14 <- F14modelsArranged %>% 
  dplyr::slice(1)


```


# SCREEN 14
## OVERSIZE

```{r}
OS14Pred <- Screen14modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'OS')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) 

OS14RRCoefD <- glancedReg14%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'OS')) %>%  
    dplyr::select( glanced = glanced_RR)

 OS14GGSCoefD <- glancedReg14%>% 
  ungroup() %>% 
   dplyr::filter(stringr::str_detect(stream,'OS')) %>%
   # dplyr::slice(3) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
OS14modelsArranged <-  rbind(OS14RRCoefD,OS14GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = OS14Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestOS14 <- OS14modelsArranged %>% 
  dplyr::slice(1)
```

# SCREEN 14
## UNDERSIZE

```{r}
US14Pred <- Screen14modelOutput %>% 
  dplyr::filter(stringr::str_detect(stream,'US')) %>% 
  dplyr::select(-1) %>% #column
  t() %>% 
  as_tibble()%>% 
  dplyr::rename("Predict" = V1) 

US14RRCoefD <- glancedReg14%>% 
   ungroup() %>% 
  dplyr::filter(stringr::str_detect(stream,'US')) %>%  
    dplyr::select( glanced = glanced_RR)

 US14GGSCoefD <- glancedReg14%>% 
  ungroup() %>% 
   dplyr::filter(stringr::str_detect(stream,'US')) %>%
   # dplyr::slice(5) %>% 
   dplyr::select(glanced = glanced_GGS,)

 #combine rows of all models. NOw all the models have the same col names, so i can add the prediction values in a new col.
US14modelsArranged <-  rbind(US14RRCoefD,US14GGSCoefD) %>% 
  unnest() %>% 
  #rename rows and select those required:
   mutate(model = modellist) %>% # "modellist" created above
   mutate(Predict = US14Pred$Predict) %>% 
   dplyr::select(model,Predict, r.squared, adj.r.squared, AIC) %>% 
 #sort according to RSquared:
  arrange(desc(adj.r.squared))

#Best for Stream1

BestUS14 <- US14modelsArranged %>% 
  dplyr::slice(1)


```

