
# Screening efficiencies and comparison



```{r, include = FALSE}
#Function here::here to help with file paths relative to the project folder:
library("here")
```

```{r, include = FALSE }
#attach rpackages from central location:
source(here::here("02_rpackages",'projectpackages.R'))
```
```{r echo = FALSE}
BestF13 <- read.csv(here::here("03_code/01_code-output", "BestF13.csv"))
BestOS13 <- read.csv(here::here("03_code/01_code-output", "BestOS13.csv"))
BestUS13 <- read.csv(here::here("03_code/01_code-output", "BestUS13.csv"))

BestF14 <- read.csv(here::here("03_code/01_code-output", "BestF14.csv"))
BestOS14 <- read.csv(here::here("03_code/01_code-output", "BestOS14.csv"))
BestUS14 <- read.csv(here::here("03_code/01_code-output", "BestUS14.csv"))
```


## Derrick Method

Let:


A	<- Percent of oversize in the feed 

B	<- Percent of undersize in the feed 

C	<- Percent of oversize in the oversize product 

D	<- Percent of undersize in the undersize product 

Then:

U  <- Undersize weight percent

O  <- Oversize weight percent

EU <- Undersize efficiency

Eo <- Oversize efficiency

E  <- Overall efficiency



```{r echo=FALSE}
#assign letters accoring to Derrick efficiency formula:  
Screen <- 13

A <- 1-BestF13$Predict
B <- BestF13$Predict
C <- 1- BestOS13$Predict
D <- BestUS13$Predict
```

### Derick efficiency formulation
```{r}
U <- (C-A)/(C+D-1)
O <- 1 - U
Eu <- U*D/B
Eo <- O*C/A
E <- U*D+O*C/100
```


```{r echo=FALSE}
Screen13Efficiency <- cbind(Screen,A,B,C,D,U,O,Eu,Eo,E) %>% 
  as_tibble() 
  
```


```{r echo=FALSE}
Screen <- 14

A <- 1-BestF14$Predict
B <- BestF14$Predict
C <- 1- BestOS14$Predict
D <- BestUS14$Predict

U <- (C-A)/(C+D-1)
O <- 1 - U
Eu <- U*D/B
Eo <- O*C/A
E <- U*D+O*C/100
    
Screen14Efficiency <- cbind(Screen,A,B,C,D,U,O,Eu,Eo,E) %>% 
  as_tibble() 

```

Combining the two efficiency outputs

```{r echo = FALSE}
Efficiencies <- rbind (Screen13Efficiency,Screen14Efficiency)
```

```{r}
Efficiencies
```



