---
output:
  pdf_document: default
  html_document: default
---
This file houses most of the code for this specific test conducted.
the filename (of this file) denotes the specific test which's code is represented here.
the raw_psd data is pulled into this file and processed.
data munging/wrangling ocurrs here mainly.
the outputs from this file is used within or drawn into the various chapters and subsequently into the final file (base.Rmd) for conversion to PDF (currently not HTML).
outputs are exported or written to code/01_code-outputs.

```{r, include = FALSE}
#Function here::here to help with file paths relative to the project folder:
library("here")
```


```{r,include = FALSE }
#attache rpackages from central location:
source(here::here("02_rpackages",'projectpackages.R'))

```

```{r}
#various options that controle chunk and graphics:

knitr::opts_chunk$set(echo = FALSE, warning=FALSE,message=FALSE)
knitr::opts_chunk$set(fig.align="center") #default align for figures
#devtools::install_github("username/packagename")
knitr.table.format = "latex" #global option for tables. can still set any in each kable function.
#excellent for LaTeX equaitons:(probable keep this in bib)
#http://visualmatheditor.equatheque.net/VisualMathEditor.html
```

```{r}
#pull in the data, try to give descriptive name: in this case 'gramdata'.

gramdata <- read_csv(here("01_data/02_preparedData", "test-31aug-2014-csv.csv")) #read here to see ,ore about "here::here" function (https://malco.io/2018/11/05/why-should-i-use-the-here-package-when-i-m-already-using-projects/)

```

```{r}

#save imported data as a tibble..convenient type of data frame for further processing.
gramdata <- as_tibble(gramdata)

# each screen has 5 decks and here ill average these. "deck_0" is a sample taken from the distributor that feeds the screen and thus represents all 5 decks. in this excercise ill combine the distributor sample with th decks to compile a mean.

# In this excercise ill focus on the means of the distributions.
#separating x and y eases calculation steps 

sieve <- gramdata %>% 
  select(1) %>% 
  as_tibble(as.data.frame(.))
#now to save the out put so it cab reused in the report:
# there no confusion when i use the term "takeout" (like pizza) i.e. take from here to smw else.
# simmilarlt, Im trying "BrinIn" on the other end (the child of the mother file where this code will be brought in .)
##I should have a lis tin thie beginning  of this script detailing a list of these depencansies, so one can see at 1st glance the risk of changing code.
##as well as (maybe) a key section detailing terms used for objects.
```

```{r}

takeOut_sieve <- here("03_code/01_code-output","sieves-used-in-psd.txt")
write.table(sieve, takeOut_sieve, sep=",", row.names = FALSE, quote = FALSE)
#dependents / use in: methodSection.Rmd.
```


```{r}
#excluding the sieve (first) column (x axis).
gramdata1 <- gramdata %>%
  dplyr::select(-1) %>%   #dplyr::select(2:ncol(.)) %>%
  as_tibble()

#calculating %mass retained for all samples.

pct <- gramdata1 %>% #mass percentage
  mutate_all ( ~(./sum(.)))
```


```{r}
#in this script, feed stream PSD results separated from that of Over and undersize.
#calculate means in the same step with dplyr::select function.

# Means of streams frequency distribution 


# Two plant screen tested for comparison. Each plant screen has 5 decks.
# In this test we'll average the results of the five decks. We can (and should) also have a look at the variability between the 5 decks to see if all results look plausible.
#The two screen are called "screen13" and "screen14".
#Results of screen13's feed samples are located in columns 1:6, thus we select columns 1:6 and calculate their withi the dplyr's mutate function.
feed13 <- pct %>% 
  dplyr::select(1:6) %>%   #check in the data which columns contain the data stream to be averaged.
  mutate(Feed13MeanPct = rowMeans(.)) #mutate creates the new colu,m with mean mass percent data.

#pull this mean column out as a vector to use later:
Feed13MeanPct <- feed13$Feed13MeanPct 

#underpan from screen 13 only allowed for 1 sample to be taken and this sample represent all the decks and thus we rename it as the mean.
US13MeanPct <- pct %>%  
  dplyr::select(US13_0, "US13MeanPct" = "US13_0") 

osize13 <- pct %>% 
  dplyr::select(8:12) %>% 
  mutate(OS13MeanPct=rowMeans(.))
OS13MeanPct <- osize13$OS13MeanPct
```

```{r}
#do same for screen 14

feed14 <- pct %>% 
  dplyr::select(13:18) %>%   #check in the data which columns contain the data stream to be averaged.
  mutate(Feed14MeanPct = rowMeans(.)) #mutate creates the new colu,m with mean mass percent data.
Feed14MeanPct <- feed14$Feed14MeanPct


US14MeanPct <- pct %>%  
  dplyr::select(US14_0, "US14MeanPct" = "US14_0") 

osize14 <- pct %>% 
  dplyr::select(20:24) %>% 
  mutate(mean_pct = rowMeans(.)) 
OS14MeanPct <- osize14$mean_pct
```

plotting raw_psd feed distribution to have a quick view if they are simmilar. if they are not (simmilar) then the expeririment or test will not not give conclusive results. as our aim is to test if one panel size is "signifficantly" better than another panels size.

```{r }
feedraw_psd <- cbind(sieve, Feed13MeanPct, Feed14MeanPct) 
OSraw_psd <- cbind(sieve, OS13MeanPct, OS14MeanPct)  
USraw_psd <- cbind(sieve, US13MeanPct, US14MeanPct)
```
```{r }
write.table(feedraw_psd, here("03_code/01_code-output","feedraw_psd.txt"), sep=",", quote = FALSE)
write.table(OSraw_psd, here("03_code/01_code-output","OSraw_psd.txt"), sep=",", quote = FALSE)
write.table(USraw_psd, here("03_code/01_code-output","USraw_psd.txt"), sep=",", quote = FALSE)

#long format prep for plot
#this code is duplicated (convert to long data and plots) in "results-and-discussionSEction".. here for prior checking, there for report inclusion.

long_feedraw_psd <- feedraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")
long_OSraw_psd <- OSraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")  
long_USraw_psd <- USraw_psd %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")

#combine the datasets:
PSD_raw_psd_allStreams <- rbind(long_feedraw_psd,long_OSraw_psd,long_USraw_psd)
PSD_raw_psd_allStreams <- data.frame(PSD_raw_psd_allStreams,
                             Df = rep(c("Feed (unmodeled)","OS (unmod.)","US (unmod.)" ),
                                                      times=c(nrow(long_feedraw_psd),nrow(long_OSraw_psd),nrow(long_USraw_psd))))

(outplot_all_unmodelled <- ggplot(PSD_raw_psd_allStreams, aes(sieve, probability, colour = stream)) +
  geom_line(size = 1) +
  geom_point() +
  ggtitle("Feed streams unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df)) #facet wrap allow for multiple plots next to eachother, whil eusing common axes for all plots.
```

```{r}
#save the plot as image:
ggsave(here("05_fig_output","allStreamsPreModelling.png"), outplot_all_unmodelled, width=10, height=8)

#dependents: methodSection
```
feed streams' psd look close enough in this test.

```{r}
#cummulative data for plots
#for cumsum ..do before convert to long format

feedraw_cum <- feedraw_psd %>% 
  mutate (CumRet_F13 = cumsum(Feed13MeanPct)) %>%
  mutate (CumPass_F13 = 1-CumRet_F13) %>% 
  mutate (CumRet_F14 = cumsum(Feed14MeanPct)) %>%
  mutate (CumPass_F14 = 1-CumRet_F14)
  

OSraw_cum <- OSraw_psd %>% 
  mutate (CumRet_OS13 = cumsum(OS13MeanPct)) %>%
  mutate (CumPass_OS13 = 1-CumRet_OS13) %>% 
  mutate (CumRet_OS14 = cumsum(OS14MeanPct)) %>%
  mutate (CumPass_OS14 = 1-CumRet_OS14)

USraw_cum <- USraw_psd %>% 
  mutate (CumRet_US13 = cumsum(US13MeanPct)) %>%
  mutate (CumPass_US13 = 1-CumRet_US13) %>% 
  mutate (CumRet_US14 = cumsum(US14MeanPct)) %>%
  mutate (CumPass_US14 = 1-CumRet_US14)

#select the columns to plot
#in this case: cumpass
feedRawCumOnly <- feedraw_cum %>% 
  select(sieve, CumPass_F13, CumPass_F14)

OSRawCumOnly <- OSraw_cum %>% 
  select(sieve, CumPass_OS13, CumPass_OS14)

USRawCumOnly <- USraw_cum %>% 
  select(sieve, CumPass_US13, CumPass_US14)

#long format for ggplot
long_feedraw_cum <- feedRawCumOnly %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")
long_OSraw_cum <- OSRawCumOnly %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")  
long_USraw_cum <- USRawCumOnly %>% pivot_longer(-sieve, names_to= "stream" , values_to = "probability")

#combine the datasets: (to ease side by side plot in ggplot)
PSD_raw_cum_allStreams <- rbind(long_feedraw_cum,long_OSraw_cum,long_USraw_cum)
PSD_raw_cum_allStreams <- data.frame(PSD_raw_cum_allStreams,
                             Df = rep(c("Feed (unmodeled)","OS (unmod.)","US (unmod.)" ),
                                                      times=c(nrow(long_feedraw_cum),nrow(long_OSraw_cum),nrow(long_USraw_cum))))

(plot_all_unmodelled_cum <- ggplot(PSD_raw_cum_allStreams, aes(sieve, probability, colour = stream)) +
  geom_line(size = 1) +
  geom_point() +
  ggtitle("Cummulative unmoddeled solids frequency distributions.") +
  theme(plot.title = element_text(size=9)) +
  facet_wrap(~Df)) #facet wrap allow for multiple plots next to eachother, whil eusing common axes for all 

#save the plot as image:
ggsave(here("05_fig_output","allStreamsCummulativePreModelling.pdf"), plot_all_unmodelled_cum, width=10, height=8)

#dependents: methodSection

```






```{r}
#bring all the screen stream means together.
#In the following steps, transformations are applied. these transformations involve double logs. as these logs  will be applied to cummulative percentage values, the last and largest will be 1, and log of 1 is 0, and the second log (log of 0) is "-inf,
#thus i''ll exclude the last row using dplyr::slice (::filter does work anymore (tidyverse update)).

meanpct <- cbind(sieve, Feed13MeanPct, OS13MeanPct, US13MeanPct, Feed14MeanPct, OS14MeanPct, US14MeanPct)

#here the vector "meanpct" contains all stream averages. In certain circumstances this would suffice. In this case, its doesnt: 
# the streams US13MeanPct and US14MeanPct have zero mass retained in the first bin of the particle size distribution (largest screen). 
#We know we're going to use log transforms and logs of zero mass = -Inf. 
#Thus we'll have to apply our models separately to the two parts of our data (due to their difference in vector lengths).
# i'll keep vector "meanpct" but also separate them and then apply the linear models on the two groups separately:
#there must a shorter way to ignore nas..[add to to do]
#maybe a good idea is to separate them from the data indraw step thus excel.
meanPct_FeedAndOS <- cbind(sieve, Feed13MeanPct, OS13MeanPct, Feed14MeanPct, OS14MeanPct)

sieve_sliced <- sieve %>% 
  dplyr::slice(2:n()) #also have to prepare the x(sieve) vector to be the same n() as y (in the case of the undersize streams).(https://dplyr.tidyverse.org/reference/slice.html)

sliced_US13MeanPct <- US13MeanPct %>% 
  dplyr::slice(2:n())

sliced_US14MeanPct <- US14MeanPct %>% 
  dplyr::slice(2:n())

#combine the sliced vectors 
meanPct_US <- cbind(sieve_sliced, sliced_US13MeanPct, sliced_US14MeanPct)

#the work done here ontop is not automated and the engineer has to look-think-do depending on the data.

#As we have two 'sets' of data primarily because of different lengths of data points (1st screen pan had 0 grams in the largest size fraction for the Us samples),
#thus we'll do two code sets of regressions separately. Done simmilarly but just separately..we've already prepared the data ontop.

```







```{r}
#rearange in long format (tidy data) to enable grouping in following step.    
#"pivot_longer" function renders data compatable with tidyverse plotting and analases

long_meanPct_FeedAndOS <- meanPct_FeedAndOS %>% 
  pivot_longer(-sieve, names_to= "stream" , values_to = "probability") # opposite is :pivot_wider(names_from= stream, values_from = probs). use quotes when names do not yet exist, if exist ,; no quotes.

long_meanPct_US <- meanPct_US %>% 
  pivot_longer(-sieve, names_to= "stream" , values_to = "probability") 

#plot
#feed and OS
#adding the () arround the entire function will execute the plot as well as display (print) it


```

```{r}
#here the cummulative passing and retained mass percentages of each stream is calculated (with dplyr::mutate),
#followed by applied the Rosin Rammler- as well as the Gates-Gaudin-Schumann distribution transformations.
#the formulas are descibed in the .rmd writeup in Latex.
transformations1 <- long_meanPct_FeedAndOS %>% 
  group_by (stream)%>% 
  mutate (cumret = cumsum(probability)) %>%
  select (-probability) %>%
  dplyr::slice(1:11) %>% #dplyr::filter worked here previously, but now doesn't anymore. dplyr::slice works with exact same syntax as ::filter did.
  mutate (cumpass = 1-cumret) %>%
    #Rosin Rammler transforms:
  mutate (
    RRx = log(sieve),
    RRy = log(log(1/cumret)),
    # Gauss Gaudin Shumann transforms:
    GGS_x = log(sieve),
    GGS_y = log(cumret))  %>%
  
  mutate_if(is.numeric, list(~na_if(., -Inf)))%>% #removes -Infinities and replace with NA. This required as we took logs of 0 (sieve) and 1 (cumret).
  nest() 
# Nesting is often useful for creating per group models

transformations2 <- long_meanPct_US %>% 
  group_by (stream)%>% 
  mutate (cumret = cumsum(probability)) %>%
  select (-probability) %>%
  dplyr::slice(1:10) %>% #i select rows 1 to 10 as we've already removed row1 in the previous step with 'slice' 2:n(). 
  mutate (cumpass = 1-cumret) %>%
  #Rosin Rammler transforms:
  mutate (
    RRx = log(sieve),
    RRy = log(log(1/cumret)),
    # Gauss Gaudin Shumann transforms:
    GGS_x = log(sieve),
    GGS_y = log(cumret))  %>%
  
  mutate_if(is.numeric, list(~na_if(., -Inf)))%>% #removes -Infinities and replace with NA. This required as we took logs of 0 (sieve) and 1 (cumret).
  nest() 
```







```{r}

#continuing with two sets, we'll have two sets of regressions:
regression1 <- transformations1 %>% 
  mutate(
    #RRmodel
    #tidy, glance and augment are funtions from the broom package that helps extraxt model details.
    RRmodels = lapply(data, function(df) lm(RRy ~ RRx, data = df)),# "RRmodels" column will be created in the mutate.
    tidied_RR = map (RRmodels, tidy), 
    glanced_RR = map(RRmodels, glance),
    augmented_RR = map (RRmodels, augment),
    
    #GGS model    
    GGS_models = lapply(data, function(df) lm(GGS_y ~ GGS_x, data = df)),# "GGS_models" column will be created in the mutate.
    tidied_GGS = map (GGS_models, tidy), 
    glanced_GGS = map(GGS_models, glance),
    augmented_GGS = map (GGS_models, augment)
  ) 




regression2 <- transformations2 %>% 
  mutate(
    #RRmodel
    #tidy, glance and augment are funtions from the broom package that helps extraxt model details.
    RRmodels = lapply(data, function(df) lm(RRy ~ RRx, data = df)),# "RRmodels" column will be created in the mutate.
    tidied_RR = map (RRmodels, tidy), 
    glanced_RR = map(RRmodels, glance),
    augmented_RR = map (RRmodels, augment),
    
    #GGS model    
    GGS_models = lapply(data, function(df) lm(GGS_y ~ GGS_x, data = df)),# "GGS_models" column will be created in the mutate.
    tidied_GGS = map (GGS_models, tidy), 
    glanced_GGS = map(GGS_models, glance),
    augmented_GGS = map (GGS_models, augment)
  ) 

```

```{r}
#####

#unnest two list at sme gives issues after dplyr update? 
#so for now we'll unnest individually..

# tidy_reg_RR_GGS_1 <-regression1 %>% 
#   unnest(c(tidied_RR,tidied_GGS))

#exctract regression analasese twice
#once for both parts of regression1
tidy_reg_RR_1 <-regression1 %>% 
  unnest(tidied_RR)

tidy_reg_GGS_1 <-regression1 %>% 
  unnest(tidied_GGS)

#once for both parts of regression2
tidy_reg_RR_2 <-regression2 %>% 
  unnest(tidied_RR)

tidy_reg_GGS_2 <-regression2 %>% 
  unnest(tidied_GGS) 

```

# the required regression data is now unnested but mixed with all the other lists and data.
#now pull out or select the relevent data.

#i do quick check if i can print tables in .rmd mother report (currently named "grams3-report-name.RMD")
# to prevent the .RMD file to all the script from this .R script, we help .RMD identify wich code to use:

```{r}
Coef_RR1 <- tidy_reg_RR_1 %>% 
  dplyr::select(stream,term, estimate)


## @knitr coefprint1
table_RR1Coef_RR1 <-Coef_RR1%>% kable

## @knitr coefprint2
## @knitr coefprint3


Coef_RR2 <- tidy_reg_RR_2 %>% 
  dplyr::select(stream,term, estimate)

Coef_GGS1 <- tidy_reg_GGS_1 %>% 
  dplyr::select(stream,term, estimate)

Coef_GGS2 <- tidy_reg_GGS_2 %>% 
  dplyr::select(stream,term, estimate)

```
#it might be worth it to separate each stream's coefficients in its own dataframe.
#this should ease creation or presentation of the regression formulas.


```{r}

glanced_reg_RR_1 <-regression1 %>% 
  unnest(glanced_RR)

glanced_reg_GGS_1 <-regression1 %>% 
  unnest(glanced_GGS)

#once for both parts of regression2
glanced_reg_RR_2 <-regression2 %>% 
  unnest(glanced_RR)

glanced_reg_GGS_2 <-regression2 %>% 
  unnest(glanced_GGS)
```

```{r}
#statistical measures of model fit.
#CLeaning up the glanced data and only selecting the output required for presentation.
#Coefficient of determination (r^2).(i tried latex formatting for the R2 not yet successful)
coef_deter_RR1 <- glanced_reg_RR_1 %>% 
  #conduct select and rename in one step with dplyr::select()
 select(stream,R2 = r.squared, adj.R2= adj.r.squared, p.value, AIC)

coef_deter_RR2 <- glanced_reg_RR_2 %>% 
  select(stream,R2 = r.squared, adj.R2= adj.r.squared, p.value, AIC)

coef_deter_GGS1 <- glanced_reg_GGS_1 %>% 
  select(stream,R2 = r.squared, adj.R2= adj.r.squared, p.value, AIC)

coef_deter_GGS2 <- glanced_reg_GGS_2 %>% 
  select(stream,R2 = r.squared, adj.R2= adj.r.squared, p.value, AIC)

R2_RR <- full_join(coef_deter_RR1,coef_deter_RR2)
R2_GGS <- full_join(coef_deter_GGS1,coef_deter_GGS2)

#write the tibbles to \01_code-output folder  for use in table generated in resultsanddiscion section
write.table(R2_RR, file = here("03_code/01_code-output","R2_RR.txt"), sep=",", quote = FALSE)
write.table(R2_GGS, file = here("03_code/01_code-output","R2_GGS.txt"), sep=",", quote = FALSE)
```

```{r}

#print the out put of the table.
# bring in the saved data to be tabled:
R2_RR <- read.csv(file = here::here("03_code/01_code-output","R2_RR.txt"))
R2_GGS <- read.csv(file = here::here("03_code/01_code-output","R2_GGS.txt"))

tblR2RR <- knitr::kable(R2_RR,
                        "latex",
                        escape = F,booktabs = T, 
                        digits = c(0,3,3,4,1)) %>% 
  column_spec(1:5, width = "1.2cm") 
  #this column_spec is supposed to set column widths to force text to wrap inside the colmn #https://community.rstudio.com/t/wrap-column-name-in-pdf-table-from-knitr-kable/3278/4)
                        #caption="RR Model(formula)") # %>%
#  kable_styling(c("striped", "bordered"), 
                #full_width = F) %>% 
#https://www.rdocumentation.org/packages/kableExtra/versions/1.1.0/topics/column_spec


tblR2GGS <- knitr::kable(R2_GGS,
                  "latex",
                  escape = F, booktabs = T, 
                  digits = c(0,3,3,4,1)) %>% 
  column_spec(1:5, width = "1.2cm")
                  #caption="GGS Model(formula)") %>%
#kable_styling(c("striped", "bordered"), 
              #full_width = F) %>% 

# t1 <- kable(R2_RR, format = "latex", booktabs = TRUE)
# 
# t2 <- kable(R2_GGS, format = "latex", booktabs = TRUE)

cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{RR Model(formula)}
      \\centering",
        tblR2RR,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{GGS Model(formula)}",
        tblR2GGS,
    "\\end{minipage} 
\\end{table}"
))  


```

```{r}
# tidy_reg_RR_GGS%>% 
#   unnest (glanced_RR)
# tidy_reg_RR_GGS%>% 
#   unnest(augmented_RR)





# coefs <- tidy_reg_RR_GGS %>% 
#   select (stream, term, estimate, term1, estimate1)
# 
# coefs_rr <- tidy_reg_RR_GGS %>% 
#   select (stream, term, estimate)
# 
# coefs_ggs <- tidy_reg_RR_GGS %>% 
#   select (stream, term1, estimate1)


# kable(gr2, format = "html") %>% 
#   kable_styling(c("striped", "bordered"), full_width = F)%>% 
#   add_header_above(c(' ', 'r.sqaured' = 2, 'adj. r.sqaured' = 2))

#change to a wider format 
coef_wider <- coefs_rr %>% 
  pivot_wider(names_from = stream, values_from = estimate) 

coef_names1 <- coef_wider %>% 
  select("term")

coefs_intcpt_slope <- coef_wider %>% 
  select(-"term") %>% 
  t() %>% 
  as_tibble(rownames = "stream") 
#rename column names
names(coefs_intcpt_slope) <-c("stream", "intcpt", "slope")

# calc the RR scale paramater for use in percentile of back transformed distributions
coefs_intcpt_slope_scale <- coefs_intcpt_slope %>% 
  mutate(scale = exp(-intcpt/slope))


#with rownames as colnames
coefs_intcpt_slope_scale1 <-coefs_intcpt_slope_scale %>% 
  #set streams column at rownames
  column_to_rownames("stream")

kable(coefs_intcpt_slope_scale1, digits = 3)



#prepare for back transformation

#Declare function for back transformation:
# back_trform_funct_RR = function(x){
#   exp(-exp(x))
# }

Perc <- c(seq(0.95, 0.05, -0.05))
size <- ??????? 
  
  
  reg_with_fittedRR <- regression %>%
  unnest(augmented_RR) %>% 
  mutate(fitted_RR = exp(-exp(.fitted))) 



s <- reg_with_fittedRR %>% 
  select(stream,RRx,RRy,.fitted,fitted_RR) %>% 
  mutate(x = exp(log(RRx)),
         y = exp(-exp(RRy)))


ss <- s %>%  
  group_by(stream) %>% 
  nest()
```

```{r}
# join the table containing data and model transformation with coeficients.
#sss <- dplyr::left_join(ss, coefs_intcpt_slope_scale, by = "stream") 

#error from here on (cannot find "unnest_sss)
# unnest_sss <- sss %>% 
#   unnest() %>% 
#   select(stream,x,y,everything()) # rearange columns
# 
# 
# #details for adding caption
# caption <- (strwrap("Modeled PSD overlaying unnoddeled Cummulative passing distribution."))
# 
# ggplot(unnest_sss, aes(x = x, y = y, shape = stream)) +
#   
#   geom_point()+ 
#   annotate( #annotate for adding the caption.
#     geom = "text", x = 1.00, y = 1.00,    #(x = xrng[1], y = yrng[2],) i mannually tiped the y=1.oo um in here to move the caption to start at 1um and not on top of the plots at 0 um as the rng(range) arguments would do.
#     label = caption, hjust = 0, vjust = 0, size = 3
#   )
# 
# 
# 
# #y vs fitted y:
# 
# caption <- (strwrap("Observed (y-axis) VS predicted (x-axis) Cummulative passing distributions."))
# 
# ggplot(unnest_sss, aes(x = fitted_RR, y = y, shape = stream)) +
#   
#   geom_point()+ #geom_smooth() +
#   annotate( #annotate for adding the caption.
#     geom = "text", x = 1.0, y = 1.00,    #(x = xrng[1], y = yrng[2],) i mannually tiped the y=1.oo um in here to move the caption to start at 1um and not on top of the plots at 0 um as the rng(range) arguments would do.
#     label = caption, hjust = 1.25, vjust = 0, size = 3
#   )
# 
# 
# #y- and fitted y vs x:
# 
# caption <- (strwrap("Observed and predicted Cummulative passing distributions."))
# 
# ggplot() +
#   geom_point ( aes(x = x, y = y), unnest_sss) +
#   geom_smooth ( aes(x = x, y = fitted_RR), unnest_sss) +
#   
#   annotate( #annotate for adding the caption.
#     geom = "text", x = 10, y = 1.00,    
#     label = caption, hjust = 0, vjust = 0, size = 3
#   )
# 
# 
# 
# 
# 

```

