---
output:
  pdf_document: default
  html_document: default
---
Aim of this file:
Generate table (r-saquared) for chapter (child) input to base.Rmd (mother)

Reason: i cant get the table to gerate from within a code chunk or r.script, but only once knitted does the table show.., so for now i 'll keep it sepparate here in this (its own) .Rmd.

This file:

+ reads code from: "02_rpackages",'projectpackages.R' for libraries.
+ reads code from: "03_code/01_code-output","R2RR.csv"
+ reads code from: "03_code/01_code-output","R2GGS.csv"

and

+ outputs code to: 05_Results-and-discussion.Rmd



```{r, include = FALSE}
#Function here::here to help with file paths relative to the project folder:
library("here")
```


```{r, include = FALSE }
#attache rpackages from central location:
source(here::here("02_rpackages",'projectpackages.R'))

```


```{r, include = FALSE }
#the original code (displayed below is from the code file: "screentest-19oct2014.Rmd"). another copy is in a code testing file:" testSideBySidePlot.Rmd.
#here this table geerating code is kept in its own child Rmd file, a i could not get it to save a table for simple inclusion into the results discussion section. Having the code in oits own rmd file generates the pdf of the table only , and this way there is an image file of the table.

```


```{r echo = FALSE, results='asis'}

# bring in the saved data to be tabled:
R2RR <- read.csv(file = here::here("03_code/01_code-output","R2RR.csv"))
R2GGS <- read.csv(file = here::here("03_code/01_code-output","R2GGS.csv"))

tblR2RR <- knitr::kable(R2RR,
                        "latex",
                        escape = F,booktabs = T, 
                        digits = c(0,3,3,4,1)) %>% 
  column_spec(1:5, width = "0.9cm") %>% 
  column_spec(1, width = "2.3cm")
  #this column_spec is supposed to set column widths to force text to wrap inside the colmn #https://community.rstudio.com/t/wrap-column-name-in-pdf-table-from-knitr-kable/3278/4)
                        #caption="RR Model(formula)") # %>%
#  kable_styling(c("striped", "bordered"), 
                #full_width = F) %>% 
#https://www.rdocumentation.org/packages/kableExtra/versions/1.1.0/topics/column_spec


tblR2GGS <- knitr::kable(R2GGS,
                  "latex",
                  escape = F, booktabs = T, 
                  digits = c(0,3,3,4,1)) %>% 
  column_spec(2:5, width = "0.9cm") %>% 
  column_spec(1, width = "2.3cm")
                  #caption="GGS Model(formula)") %>%
#kable_styling(c("striped", "bordered"), 
              #full_width = F) %>% 

# t1 <- kable(R2RR, format = "latex", booktabs = TRUE)
# 
# t2 <- kable(R2GGS, format = "latex", booktabs = TRUE)

#code posistions 2 tables side by side
cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{RR Model(formula)}
      \\centering",
        tblR2RR,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{GGS Model(formula)}",
        tblR2GGS,
    "\\end{minipage} 
\\end{table}"
))  



```