packages
this is the central place where this project will attach packages from.
allpackeges are accumulated here (manualy).

the reason for doing this is to avoid duplicating all packages across all files.
this eases knitting from both the 'mother-' or base.Rmd and knitting from individual files as well.
add new packes in the list below names "mypackages" then
run the chunck code. the chunk will write a csv file that the other files contained within the prject folder will read and attach. 

```{r mypackage}

library(easypackages)
library(here)

mypackage <- c("rmd","patchwork","tidyverse","kableExtra","conflicted","tinytex","tidyverse","readxl","modelr","broom","reshape","readr","knitr","kableExtra","magrittr","qwraps2","xtable","gridExtra")

libraries(mypackage) #attaches packages
packages(mypackage) #checks installed, installs, attaches.
```


Run the following code to update the package list after new packages have been added.

```{r}

write.table(mypackage, file = here::here("rpackages","mypackage.txt"), sep=",", quote = TRUE,row.names = FALSE)

```
