---
output:
  pdf_document: default
  html_document: default
---
# Results and Discussion


```{r, include = FALSE}
#Function here::here to help with file paths relative to the project folder:
library("here")
```


```{r,include = FALSE }
#attache rpackages from central location:
source(here::here("rpackages",'projectpackages.R'))

```


```{r include = FALSE}

options(qwraps2_markup = 'markdown')

knitr.table.format = "latex" #global option for tables. can still set any in each kable function.

#excellent for LaTeX equations:(probable keep this in bib)
#http://visualmatheditor.equatheque.net/VisualMathEditor.html
```
<br><br><br><br>

```{r global_options, R.options=knitr::opts_chunk$set(warning=FALSE, message=FALSE)}
```

Each test's feed stream PSD results were first compared to confirm that their distributions were simmilar to allow for comparitive statictics.  

```{r echo=FALSE}
BringIn_file <- here::here("code/code-output","long_feedraw.txt") #results generated in screentest-19oct2014.R
longfeedraw <- read.csv(file = BringIn_file)


ggplot(longfeedraw, aes(sieve, probability, colour = stream)) +
  geom_line()+
  ggtitle("Feed stream unmoddeled solids frequency distribution.") +
  theme(plot.title = element_text(size=9))
  #annotate(caption) geom = "text", x = 1.00, y = 1.00,


 
#         #(x = xrng[1], y = yrng[2],) i mannually tiped the y=1.oo um in here to move the caption to start at 1um and not on top of the plots at 0 um as the rng(range) arguments would do.
#     label = caption, hjust = 0, vjust = 0, size = 3
#   )
# 
```

The two most commmonly used distributions in Geology and Mineral Processing and specifically comminution circuits are the Roslin-Rammler and the Gates-Gaudin-Schumann distributions.

Both models were used  to model all PSD screening data to, and the subsequent best fit model was selected in each case. Model selection was determined by comparing each PSD's transformed linear model's determinant ($R^2$).

RR model fits the feed streams means (F13m and F14m) better (near straight line QQ fits) than the Oversize streams.


If the transformed size distributions from a crushing or grinding operation do not
approximate a straight line, it suggests that there may have been a problem with the data
collection, or there is something unusual happening in the comminution process (hang-ups or unnuasual recirculation).
The size modulus is a measure of how coarse the size distribution is, and the distribution
modulus is a measure of how broad the size distribution is. Size modulus for a size
distribution can be determined from a graph by extrapolating the straight-line portion up
to 100% passing and finding the corresponding size value. The distribution modulus can
be calculated by choosing two points in the linear portion of the graph, calculating the
logs of the sizes and % passing values, and calculating the slope. 

Interpolation betweeen measured sizing points is conducted by the back-transformation of the model-fitted points along the respective model's distribution function. 


```{r ,echo=FALSE, results='asis'}
library(knitr)
library(xtable)

# bring in the saved data to be tabled:
R2_RR <- read.csv(file = here::here("code/code-output","R2_RR.txt"))
R2_GGS <- read.csv(file = here::here("code/code-output","R2_GGS.txt"))

tblR2RR <- knitr::kable(R2_RR,
                        "latex",
                        escape = F,booktabs = T, 
                        digits = c(0,3,3,4,1)) %>% 
  column_spec(1:5, width = "1.2cm") 
  #this column_spec is supposed to set column widths to force text to wrap inside the colmn #https://community.rstudio.com/t/wrap-column-name-in-pdf-table-from-knitr-kable/3278/4)
                        #caption="RR Model(formula)") # %>%
#  kable_styling(c("striped", "bordered"), 
                #full_width = F) %>% 
#https://www.rdocumentation.org/packages/kableExtra/versions/1.1.0/topics/column_spec


tblR2GGS <- knitr::kable(R2_GGS,
                  "latex",
                  escape = F, booktabs = T, 
                  digits = c(0,3,3,4,1)) %>% 
  column_spec(1:5, width = "1.2cm")
                  #caption="GGS Model(formula)") %>%
#kable_styling(c("striped", "bordered"), 
              #full_width = F) %>% 

# t1 <- kable(R2_RR, format = "latex", booktabs = TRUE)
# 
# t2 <- kable(R2_GGS, format = "latex", booktabs = TRUE)

cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{RR Model(formula)}
      \\centering",
        tblR2RR,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{GGS Model(formula)}",
        tblR2GGS,
    "\\end{minipage} 
\\end{table}"
))  




```




try add as footnote in table/s: "RRmodel is a better fit ,according to the simple model applied, i.e. single linear model applied to transformed y-variables and transformed x-factors. When applyinh peicewise (conditional) factors, the GGS model becomes a better model, but at the same tiem more noise (errors (epsilon?) is incorpaorated in the model. double the coefficients.


```{r , echo=FALSE, results='asis', warning=TRUE}
# # Setting `results = 'asis'` allows for using Latex within the code chunk
# 
#      cat('\\begin{center}')
#      # `{c c}` Creates a two column table
#      # Use `{c | c}` if you'd like a line between the tables
#      cat('\\begin{tabular}{ c c }')
# 
#      print(tblR2RR, format = 'latex')
#      # Separate the two columns with an `&`
# 
#      cat('&')
# 
#      print(tblR2GGS, format = 'latex')
#      cat('\\end{tabular}')
#      cat('\\end{center}')
```









