---
output:
  pdf_document: default
  html_document: default
---
---
output:
  html_document: default
  pdf_document: default
  word_document: default
  ---
# Results and Discussion

```{r include=FALSE}
library(tidyverse)
library(kableExtra)
library(xtable)
library(ggplot2)
library(patchwork) #for multiple plot placement
library(gridExtra) #tables as graphics

library(here)
library(conflicted)
library(markdown)
library(tinytex)
library(tidyverse)
library(readxl)
library(modelr)
library(broom)
library(reshape)
library(readr)
library(knitr)
library(kableExtra)
library(magrittr)
library(qwraps2)
options(qwraps2_markup = 'markdown')


knitr.table.format = "latex" #global option for tables. can still set any in each kable function.

#excellent for LaTeX equations:(probable keep this in bib)
#http://visualmatheditor.equatheque.net/VisualMathEditor.html

```
<br><br><br><br>

```{r global_options, R.options=knitr::opts_chunk$set(warning=FALSE, message=FALSE)}
```



```{r echo=FALSE}
BringIn_file <- here::here("code/code-output","long_feedraw.txt")

longfeedraw <- read.csv(file = BringIn_file)

ggplot(longfeedraw, aes(sieve, probability, colour = stream)) +
  geom_line()
```

The two most commmonly used distributions in Geology and Mineral Processing and specifically comminution circuits are the Roslin-Rammler and the Gates-Gaudin-Schumann distributions.

Both models were used  to model all PSD screening data to, and the subsequent best fit model was selected in each case. Model selection was determined by comparing each PSD's transformed linear model's determinant ($R^2$).
Interpolation betweeen measured sizing points is conducted by the back-transformation of the model-fitted points along the respective model's distribution function. 


```{r echo=FALSE, results='asis'}
library(knitr)
library(xtable)

# bring in the saved data to be tabled:
R2_RR <- read.csv(file = here::here("code/code-output","R2_RR.txt"))
R2_GGS <- read.csv(file = here::here("code/code-output","R2_GGS.txt"))

tblR2RR <- knitr::kable(R2_RR,
                        "latex",
                        escape = F,booktabs = T) #, 
                        #digits = c(0,3,3,4,1), 
                        #caption="RR Model(formula)") %>%
#  kable_styling(c("striped", "bordered"), 
                #full_width = F) %>% 
  #column_spec(1:5, width = "5cm") #this column_spec is supposed to set column widths to force text to wrap inside the colmn #https://community.rstudio.com/t/wrap-column-name-in-pdf-table-from-knitr-kable/3278/4)
#https://www.rdocumentation.org/packages/kableExtra/versions/1.1.0/topics/column_spec


tblR2GGS <- knitr::kable(R2_GGS,
                  "latex",
                  escape = F, booktabs = T)#, 
                  #digits = c(0,3,3,4,1) ,
                  #caption="GGS Model(formula)") %>%
#kable_styling(c("striped", "bordered"), 
              #full_width = F) %>% 
  #column_spec(1:5, width = "2cm")

# t1 <- kable(R2_RR, format = "latex", booktabs = TRUE)
# 
# t2 <- kable(R2_GGS, format = "latex", booktabs = TRUE)

cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{}
      \\centering",
        tblR2RR,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{}",
        tblR2GGS,
    "\\end{minipage} 
\\end{table}"
))  




```


```{r ,echo=FALSE, results="asis"}
library(xtable)
library(knitr)

#side-by-side-tables
cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{}
      \\centering",
        tblR2RR,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{}",
        tblR2GGS,
    "\\end{minipage}
\\end{table}"
))


```

```{r , echo=FALSE, results='asis', warning=TRUE}
# Setting `results = 'asis'` allows for using Latex within the code chunk

     cat('\\begin{center}')
     # `{c c}` Creates a two column table
     # Use `{c | c}` if you'd like a line between the tables
     cat('\\begin{tabular}{ c c }')
     
     print(tblR2RR, format = 'latex')
     # Separate the two columns with an `&`
     
     cat('&')
     
     print(tblR2GGS, format = 'latex')
     cat('\\end{tabular}')
     cat('\\end{center}')
```





```{r sample, echo=FALSE, results='asis'}
library(knitr)
library(xtable)

t1 <- kable(R2_RR, format = "latex", booktabs = TRUE)

t2 <- kable(head(mtcars)[4:6], format = "latex", booktabs = TRUE)

cat(c("\\begin{table}[!htb]
    \\begin{minipage}{.5\\linewidth}
      \\caption{hello}
      \\centering",
        t1,
    "\\end{minipage}%
    \\begin{minipage}{.5\\linewidth}
      \\centering
        \\caption{}",
        t2,
    "\\end{minipage} 
\\end{table}"
))  
```




